Hydra Battles and Cie

### 2021-09-06 doc/part-hydras.tex
corrections chapter 7
Ordering_Functions no a class type (draft)
corrections chapters 8,9

\input{movies/snippets/Schutte_basics/iotaDemo}

@@

\begin{Coqsrc}
Axiom epsilon_statement:
  forall (A : Type) (P : A->Prop), inhabited A ->
    {x : A | (exists x, P x) -> P x}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition epsilon (A : Type) (i:inhabited A) (P : A->Prop) : A
  := proj1_sig (epsilon_statement P i).

Lemma constructive_indefinite_description :
  forall (A : Type) (P : A->Prop),
    (exists x, P x) -> { x : A | P x }.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition iota (A : Type) (i:inhabited A) (P : A->Prop) : A
  := proj1_sig (iota_statement P i).
\end{Coqsrc}

\begin{Coqsrc}
 Lemma constructive_definite_description :
  forall (A : Type) (P : A->Prop),
    (exists! x, P x) -> { x : A | P x }.
\end{Coqsrc}

\begin{Coqsrc}
Definition iota_spec (A : Type) (i:inhabited A) (P : A->Prop) :
  (exists! x:A, P x) -> P (iota i P)
  := proj2_sig (iota_statement P i).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma plus_elim (alpha : Ord) :
  forall P : (Ord->Ord)->Prop,
    (forall f: Ord->Ord, 
        ordering_function f ordinal (ge alpha)-> P f) ->
    P (plus alpha).
\end{Coqsrc}

@@

\input{movies/snippets/Critical/CrZeroAP}
\input{movies/snippets/Critical/epsilon0Cr1}

@@

\input{movies/snippets/CNF/cnfUnicity}

\input{movies/snippets/CNF/cnfExUnique}

@@

\section{How big is \texorpdfstring{$\Gamma_0$}{\texttt{Gamma0}}?}

@@

\input{movies/snippets/Gamma0/ltSto}
\input{movies/snippets/Gamma0/ltWf}
\input{movies/snippets/Gamma0/ONGamma0}

>>>>

\input{movies/snippets/Schutte_basics/iotaDemoa}
\input{movies/snippets/Schutte_basics/iotaDemob}

@@

\input{movies/snippets/MoreEpsilonIota/EpsilonStatement}

@@

\input{movies/snippets/MoreEpsilonIota/EpsilonDef}

@@

\input{movies/snippets/MoreEpsilonIota/iotaDef}

@@

\input{movies/snippets/Addition/plusElim}

@@

\inputsnippets{Critical/CrZeroAP,
  Critical/epsilon0Cr1}

@@

\inputsnippets{CNF/cnfUnicity,CNF/cnfExUnique}

@@

\section{A strict order on T2}

@@

\input{movies/snippets/Gamma0/ltSto}
\input{movies/snippets/Gamma0/ltWf}
\input{movies/snippets/Gamma0/ONGamma0}
\input{movies/snippets/Gamma0/G0z}
